О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Switch language to English
English: such that

\documentclass[a4paper,14pt]{article} %размер бумаги устанавливаем А4, шрифт 12пунктов
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel} %используем русский и английский языки с переносами
\usepackage{amssymb,amsfonts,amsmath,mathtext,enumerate,float,amsthm} %подключаем нужные пакеты расширений
\usepackage[pdftex,unicode,colorlinks=true,citecolor=black,linkcolor=black]{hyperref}
%\usepackage[pdftex,unicode,colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{indentfirst} % включить отступ у первого абзаца
\usepackage[dvips]{graphicx} %хотим вставлять рисунки?
\graphicspath{{illustr/}}%путь к рисункам

@@

\begin{document}
\renewcommand{\bibname}{Список цитированной литературы}
\renewcommand\refname{\bibname}
% !!!
% The text starts here

@@

\section{Introduction}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 - M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$.
An \textit{integral point set} in $m$-dimensional Euclidean space is such a point set $M$ that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking the fact into account, we will denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space with
$\mathfrak{M}(m,n)$ (following the notation of~\cite{our-vmmsh-2018}).
The symbol $|M|$ will be used for cardinality of $M$, i.e. the quantity of points in $M$ in our case.

@@

\begin{definition}
	For each $k > 1$, the corresponding maximal distance $m$ from Problem~\ref{problem:PPS}
	is called the $k$-th PPS coefficient and denoted by $\varphi_k$.
\end{definition}
So, it's impossible to place $k$ points in a unit square such that each pairwise distance of the points is greater than $\varphi_k$.

@@

\begin{theorem}
	For every $\varepsilon > 0$ there exists such a number $n_0$, that the inequality
	\begin{equation}
		d(2,n) \geq n\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
	\end{equation}
	holds for every $n>n_0$.
\end{theorem}

@@

%Now we need two more definitions.
\begin{definition}
	\cite{antonov2008maximal}
	A set $M\in \mathfrak{M}(m,n)$ is \textit{maximal},
	if there is no such a set $M'\in \mathfrak{M}(m,n+1)$
	that $M \subsetneq M'$.
\end{definition}

>>>>

\documentclass[a4paper,14pt]{article} %размер бумаги устанавливаем А4, шрифт 12пунктов
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel} %используем русский и английский языки с переносами
\usepackage{amssymb,amsfonts,amsmath,mathtext,enumerate,float,amsthm} %подключаем нужные пакеты расширений
\usepackage[pdftex,unicode,colorlinks=true,citecolor=black,linkcolor=black]{hyperref}
%\usepackage[pdftex,unicode,colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{indentfirst} % включить отступ у первого абзаца
\usepackage[dvips]{graphicx} %хотим вставлять рисунки?
\graphicspath{{illustr/}}%путь к рисункам

@@

\begin{document}

%\renewcommand{\bibname}{Список цитированной литературы}
%\renewcommand\refname{\bibname}
% !!!
% The text starts here

@@

\section{Introduction}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 - M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$.
An \textit{integral point set} in $m$-dimensional Euclidean space is a point set $M$ such that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking the fact into account, we will denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space with
$\mathfrak{M}(m,n)$ (following the notation of~\cite{our-vmmsh-2018}).
The symbol $|M|$ will be used for cardinality of $M$, i.e. the quantity of points in $M$ in our case.

@@

\begin{definition}
	For each $k > 1$, the corresponding maximal distance $m$ from Problem~\ref{problem:PPS}
	is called the $k$-th PPS coefficient and denoted by $\varphi_k$.
\end{definition}
So, it's impossible to place $k$ points in a unit square in such a way that each pairwise distance of the points is greater than $\varphi_k$.

@@

\begin{theorem}
	For every $\varepsilon > 0$ there exists a number $n_0$ such that the inequality
	\begin{equation}
		d(2,n) \geq n\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
	\end{equation}
	holds for every $n>n_0$.
\end{theorem}

@@

%Now we need two more definitions.
\begin{definition}
	\cite{antonov2008maximal}
	A set $M\in \mathfrak{M}(m,n)$ is \textit{maximal},
	if there is no set $M'\in \mathfrak{M}(m,n+1)$
	such that $M \subsetneq M'$.
\end{definition}
